Ice sheet mass flows

### 2024-06-05 ms.tex
Red outline for processes that change plan-view boundary
abstract rewrite

\begin{frontmatter}
\maketitle
\begin{abstract}
  Mass flows of ice sheets, and subsequent mass gains and losses, is an of-studied topic in the domain of glaciology. However, few studies consider all processes and their relative magnitudes and uncertainties - this is usually the domain of review papers. Here we present a Sankey diagram that provides an overview of all mass flow terms and processes for both the Greenlandic and Antarctic ice sheets. We use this display to highlight a) relative magnitudes among processes within ice sheets and among ice sheets and sectors, and b) the uncertainty associated with each property. We also... TBD.

  There is no new science here, but presenting existing data in new or clearer ways may still lead to new insights.
\end{abstract}
\end{frontmatter}

\section{Introduction to Sankey diagrams}

@@

>>>>

\begin{frontmatter}
\maketitle
\begin{abstract}

  Observing, quantifying, and understanding mass loss takes field observations, computer models, and insight through knowledge generation and sharing. Tabular data is optimized for computers and useful for humans, but graphical presentations can provide significantly higher information density. Here we present several Sankey diagrams depicting mass flow of ice in Greenland and Antarctica, and discuss some properties of the graphics and the cryospheric processes represented by the graphics. We focus on insight available through this choice of display, methods for estimating the various cryospheric processes, and uncertainty,
\end{abstract}
\end{frontmatter}

\section{Introduction and Background}

Mass flows of ice sheets, and subsequent mass gains and losses, is an of-studied topic in the domain of glaciology. However, few studies consider all processes and their relative magnitudes and uncertainties - this is usually the domain of review papers. Here we present a Sankey diagram that provides an overview of all mass flow terms and processes for both the Greenlandic and Antarctic ice sheets. We use this display to highlight a) relative magnitudes among processes within ice sheets and among ice sheets and sectors, and b) the uncertainty associated with each property. We also... TBD.

\subsection{Introduction to Sankey diagrams}

@@

See thick red outlines on frontal retreat and grounding line retreat. Can't be in steady state if these processes are active. Steady state may not be a natural occurrance. Could have these and be quasi-steady (cyclical).
